Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}

library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}

@@

  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
  df2$gatherings <- factor(df2$gatherings, levels = levels(df.full$gatherings))

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       	       shape = gatherings,
		       linetype = gatherings
		       ))
  p <- p + geom_point(size = 4)

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))

  #p <- p + scale_fill_manual(values = c(cols[[catal]], "darkgray"))
  #p <- p + scale_color_manual(values = c(cols[[catal]], "darkgray"))

  #   scale_color_stata() +
  #   scale_fill_stata() +
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

@@

  p <- p + #ggtitl(paste("Paper consumption (", catal, ")", sep = "")) +
         #ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +
         ggtitle(paste(c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       	 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

grid.arrange(pics[[1]], pics[[2]], top = "Figure 3", layout_matrix = matrix(c(1,2), nrow = 2, byrow=TRUE))
```

@@

pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
#print(p)
```

>>>>

```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}

common.gatherings <- setdiff(names(which(table(df.full$gatherings) > 500)), "NA")

@@

  #df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
  df2 <- filter(df2, gatherings %in% common.gatherings)  
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
  df2$gatherings <- factor(df2$gatherings, levels = levels(df.full$gatherings))

@@

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       	       shape = gatherings,
		       linetype = gatherings
		       ))

  p <- p + geom_point(size = 4)

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  #p <- p + scale_shape_manual(values = factor(common.gatherings))
  #p <- p + scale_linetype_manual(values = factor(common.gatherings))

@@

  p <- p + 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10) #+

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
title <- ggdraw() + draw_label("Figure 3", fontface='bold')
plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
```

@@

#pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
title <- ggdraw() + draw_label("Figure 4", fontface='bold')
plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
#print(p)
```
